---
title: "Propensity Score Weighting"
output: html_document
---


```{r}
library(tidyverse)
library(broom)
library(touringplans)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **exposure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

Below is the propensity score model you created in the previous exercise.

```{r, eval = TRUE}
seven_dwarfs <- seven_dwarfs_train_2018 %>%
  filter(hour == 9)

propensity_model <- glm(
  extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
  data = seven_dwarfs,
  family = binomial()
)

df <- propensity_model %>%
  augment(type.predict = "response", data = seven_dwarfs)
```

## Your Turn (Matching)

_After updating the code chunks below, change `eval = TRUE` before knitting._

Create at "matched" data set using the same propensity score model as above and a caliper of 0.2.

```{r, eval = TRUE}
library(MatchIt)

m <- matchit(extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
        data = seven_dwarfs,
        caliper = 0.2 ,
        link = "linear.logit") # ATM method


m2 <- matchit(extra_magic_morning ~ wdw_ticket_season + close + poly(weather_wdwhigh,3),
        data = seven_dwarfs,
        caliper = 0.2 ,
        link = "linear.logit") # ATM method

# Average Treatment Effect among the Matched (ATM)

matched_df <- get_matches(m) # Add "id" if there is already a variable called "id"

matched_df2 <- get_matches(m2) # Add "id" if there is already a variable called "id"
```

## Your Turn (Weighting)

_After updating the code chunks below, change `eval = TRUE` before knitting._

Add the ATE weights to the data frame, `df`

```{r, eval = FALSE}
df <- df %>%
  mutate(w_ate = (extra_magic_morning/.fitted) + ((1-extra_magic_morning)/(1 - .fitted)))

```


Stretch Goal 1: 

Add ATM weights to the data frame, `df`

```{r, eval = FALSE}
df <- df %>%
  mutate(w_atm = pmin(.fitted,1-.fitted)/((extra_magic_morning*.fitted) + 
                                           ((1 - extra_magic_morning)*(1 -.fitted))))
```

Stretch Goal 2: 

Update the code below to examine the distribution of the weighted sample. **HINT** the part that needs to be updated is the `weight` parameter in two of the `geom_histogram()` calls.

```{r, eval = FALSE}
d <- df %>%
  pivot_wider(names_from = extra_magic_morning, 
                     values_from = .fitted, 
                     names_prefix = "extra_magic_morning_p")
```


```{r, eval = FALSE, warning = FALSE}
ggplot(d) +
  geom_histogram(bins = 50, aes(extra_magic_morning_p1), alpha = 0.5) + 
  geom_histogram(bins = 50, aes(extra_magic_morning_p1, weight = w_ate), fill = "green", alpha = 0.5) + 
  geom_histogram(bins = 50, alpha = 0.5, aes(x = extra_magic_morning_p0, 
                                             y = -after_stat(count))) +  # Flip the values upside down
  geom_histogram(bins = 50, aes(x = extra_magic_morning_p0, 
                                weight = w_ate,
                                y = -after_stat(count)), fill = "blue", alpha = 0.5) + 
  ylab("count") + xlab("p") +
  geom_hline(yintercept = 0, lwd = 0.5) +
  scale_y_continuous(label = abs) +
  theme_minimal() + 
  geom_rect(aes(xmin = 0.95, xmax = 1, ymin = 5, ymax = 100), fill = "#5DB854") + 
  annotate("text", x = 0.975, y = 50, label = "trt", angle = 270, color = "white") + 
  geom_rect(aes(xmin = 0.95, xmax = 1, ymin = -100, ymax = -5), fill = "#5154B8") + 
  annotate("text", x = 0.975, y = -50, label = "control", angle = 270, color = "white")

```


```{r, eval = FALSE, warning = FALSE}
ggplot(d) +
  geom_histogram(bins = 50, aes(extra_magic_morning_p1), alpha = 0.5) + 
  geom_histogram(bins = 50, aes(extra_magic_morning_p1, weight = w_atm), fill = "green", alpha = 0.5) + 
  geom_histogram(bins = 50, alpha = 0.5, aes(x = extra_magic_morning_p0, 
                                             y = -after_stat(count))) +  # Flip the values upside down
  geom_histogram(bins = 50, aes(x = extra_magic_morning_p0, 
                                weight = w_atm,
                                y = -after_stat(count)), fill = "blue", alpha = 0.5) + 
  ylab("count") + xlab("p") +
  geom_hline(yintercept = 0, lwd = 0.5) +
  scale_y_continuous(label = abs) +
  theme_minimal() + 
  geom_rect(aes(xmin = 0.95, xmax = 1, ymin = 5, ymax = 100), fill = "#5DB854") + 
  annotate("text", x = 0.975, y = 50, label = "trt", angle = 270, color = "white") + 
  geom_rect(aes(xmin = 0.95, xmax = 1, ymin = -100, ymax = -5), fill = "#5154B8") + 
  annotate("text", x = 0.975, y = -50, label = "control", angle = 270, color = "white")

```