---
title: "Outcome Model"
output: html_document
---


```{r}
library(tidyverse)
library(broom)
library(touringplans)
library(rsample)
library(MatchIt)

seven_dwarfs <- seven_dwarfs_train_2018 %>%
  filter(hour == 9)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **exposure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

## Your turn

_After updating the code chunks below, change `eval = TRUE` before knitting._

Create a function called `ipw_fit` that fits the propensity score model from Exercise 03, incorporates the ATE weights calculated in Exercise 04, and fits a weighted outcome model.

```{r, eval = TRUE}
fit_ipw <- function(split, ...) { 
  
  .df <-analysis(split)
  
  # fit propensity score model
  
  propensity_model <- glm(formula = extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
                          data = .df,family = binomial())
  
  # calculate ATE weights
  
  .df <- propensity_model %>%
  augment(type.predict = "response", data = .df) %>% 
  mutate(w_ate = 1 / ifelse(extra_magic_morning == 0, 
                            1 - .fitted, .fitted))

  # fit correctly bootstrapped ipw model 
  lm(avg_spostmin ~ extra_magic_morning,
     data = .df, 
     weights = w_ate) %>% 
    tidy() 
}
```

Bootstrap this result 1000 times.

```{r, eval = TRUE}
set.seed(1234)

ipw_results <- bootstraps(seven_dwarfs, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_ipw)) 
```


Calculate the confidence interval

```{r, eval = TRUE}
boot_estimate <- int_t(ipw_results, results) %>% 
  filter(term == "extra_magic_morning")


boot_estimate2 <- int_bca(ipw_results, results,.fn = fit_ipw) %>% 
  filter(term == "extra_magic_morning")
```

1. int use t-student distribution
2. bca bias corrected adjustment (really complex calculation)

Stretch goal: Do the same for a model using matching.


```{r}


matchit_obj <- matchit(formula = extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
                          data = seven_dwarfs,link = "linear.logit")


.df <- get_matches(matchit_obj) # we lost a lot of observations



# Alternatives:

lm(avg_spostmin ~ extra_magic_morning,data = .df)

# In functions:


fit_matched <- function(split,...) {

  .df <- analysis(split)  
  
  matchit_obj <- matchit(formula = extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
                            data = .df,link = "linear.logit")
  
  
  .df <- get_matches(matchit_obj) # we lost a lot of observations
  
  
  
  # Alternatives:
  
  lm(avg_spostmin ~ extra_magic_morning,data = .df) %>% 
    tidy() 
}


ipw_results_matched <- bootstraps(seven_dwarfs, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_matched)) 


int_t(ipw_results_matched, results) %>% 
  filter(term == "extra_magic_morning")

```


# Interpretation

When there are extra mafic mornig you will have to wait 4 minutes longer in magic kingdom line